---
title: "Plotly Practice"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plotly

```{r}
library(tidyverse)
library(plotly)
library(p8105.datasets)

```

Analyzing NYC Airbnb data

Interactive graphics works better with smaller datasets
```{r}
data("nyc_airbnb")


nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(borough = neighbourhood_group,
         neighbourhood, stars, price, room_type, lat, long) |> 
  drop_na(stars) |> 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  )
  
```

Let's make a scatterplot!
map of nyc with all the diff airbnbs

scatterplot with just the points (marker)

text label is the thing that shows up when you hover
str_c is string combine
\n means line break

```{r}
nyc_airbnb |> 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", stars)) |> 
  plot_ly(x = ~lat, y = ~long, color = ~price, text = ~text_label,
          type = "scatter", mode = "markers", alpha = 0.5)

```

Let's make a box plot!

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

Let's make a bar plot! First do the counting step

how many airbnbs exist in each of the neighborhoods
```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
  
```


Can technically do this but don't - convert ggplot to plotly
graphic quality is not good
```{r}
ggp_scatter = 
  nyc_airbnb |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)

ggplotly(ggp_scatter)
```




